### 2020-03-11 Strings2020/strings1/strings1.tex
Add revisions & updates to strings1

	To compute $TT$ OPE, we need the OPE of $b(z)\,c(0)$; this is obtained by examining the following path integral, which is zero since the integrand is a total functional derivative:
	\begin{equation}
		0 = \int \mscr{D}b\,\mscr{D}c\,
			\fdv{\phi}\pqty{e^{-S}\,\phi}
	\end{equation}
	Taking $\phi=b,c$, this generates operator equations such as $
		\pdbar b(z)\,c(0)
		= 2\pi\delta^2(z,\bar{z})
	$. Note that $
		\pdbar(\frac{1}{z})
		= 2\pi\delta^2(z,\bar{z})
	$, which gives:
	\begin{equation}
		b(z)\,c(0) \sim c(z)\,b(0)
		\sim \frac{1}{z}
	\end{equation}

	With the $bc$ OPE in hand, the $TT$ OPE is computed directly with blunt force. This gives:
	\begin{equation}
		T(z)\,T(0)
		\sim \frac{
			-6\lambda^2 + 6\lambda - 1
		}{z^4} + \cdots
	\end{equation}
	In general we have $
		-6\lambda^2 + 6\lambda - 1
		= \frac{c}{2}
	$; for $\lambda = 2$ this gives $c = -26$. 
	\qedfull

@@

	\item[(b)(c)] Combining two $\psi$ expansions gives the mode expansion of $
		J\id{_i^j}
		= \normorder{\psi_i(z)\,\psi^j(z)}
	$:
	\begin{equation}
		J\id{_i^j}(z)
		= \sum_{k\in\mbb{Z}}
			\frac{(J\id{_i^j})_k}{z^{k+1}},\quad
		(J\id{_i^j})_k
		= \sum_{q\in\mbb{Z}+\frac{1}{2}}
			\normorder{
				b_{iq}\,b^{j\dagger}_{k-q}
			}
	\end{equation}
	It is in fact more convenient to obtain the $JJ$ OPE first, and then use it to find the  $[J_0,J_0]$ mode commutator\footnote{
		I would like to thank \textit{谷夏} for providing this hint. 
	}; note that $
		{
			{\psi}_i(z)\,{\psi}^j(w)
		}
	$ contraction gives $\frac{\delta^j_i}{z-w}$, we have:
	\begin{equation}
		J\id{_i^j}(z)\,J\id{_k^l}(0)
		\sim \frac{
			\delta_i^l\delta_k^j
		}{z^4} + \frac{
			\delta^j_k J\id{_i^l}(0)
			- \delta^l_i J\id{_k^j}(0)
		}{z},\\[1ex]
		\bqty{
			(J\id{_i^j})_0, (J\id{_k^l})_0
		}
		= \frac{1}{(2\pi i)^2}
			\oint_0 \dd{w}
			\oint_w \dd{z}
				J\id{_i^j}(z)\,J\id{_k^l}(w)
		= \delta_i^l\,(J\id{_k^j})_0
			- \delta_k^j\,(J\id{_i^l})_0
	\end{equation}

	\item[(d)] Similar to $bc$ CFT, we have:
	\begin{equation}
		T(z) = \frac{1}{2} \normorder{\psi_i\,\pd\psi^i}
			- \normorder{\pd\psi_i\,\psi^i}\,
		,\quad
		T(z)\,T(w)
		\sim \frac{n/2}{(z-w)^4}
			+ \frac{2T(w)}{(z-w)^2}
			+ \frac{\pd T(w)}{z-w}
	\end{equation}
	With each field contributing $\frac{1}{2}$ central charge.

@@

	Similar holds for $J_{ij} = \normorder{\psi_i\psi_j}$ and its OPE, but we no longer need to distinguish upper/lower indices; we have:
	\begin{equation}
		J_{ij}(z)\,J_{kl}(0)
		\sim \frac{
			- \delta_{ik}\delta_{jl}
			+ \delta_{il}\delta_{jk}
		}{z^4} + \frac{
			- \delta_{ik} J_{jl}(0)
			+ \delta_{il} J_{jk}(0)
			+ \delta_{jk} J_{il}(0)
			- \delta_{jl} J_{ik}(0)
		}{z}\\[1ex]
		\bqty{
			(J_{ij})_0, (J_{kl})_0
		}
		= - \delta_{ik} (J_{jl})_0
			+ \delta_{il} (J_{jk})_0
			+ \delta_{jk} (J_{il})_0
			- \delta_{jl} (J_{ik})_0
	\end{equation}
	This is precisely the $\mfrak{o}(n)$ algebra. 
	\qedfull

>>>>

	To compute $TT$ OPE, we need the OPE of $b(z)\,c(0)$; this is obtained by examining the following path integral, which is zero since the integrand is a total functional derivative:
	\begin{equation}
		0 = \int \mscr{D}b\,\mscr{D}c\,
			\fdv{\phi}\pqty{e^{-S}\,\psi}
	\end{equation}
	Taking $\phi,\psi=b,c$, this generates operator equations such as $
		\pdbar b(z)\,c(0)
		= 2\pi\delta^2(z,\bar{z})
	$. Note that $
		\pdbar(\frac{1}{z})
		= 2\pi\delta^2(z,\bar{z})
	$, which gives:
	\begin{equation}
		b(z)\,c(0) \sim c(z)\,b(0)
		\sim \frac{1}{z},\quad
		b(z)\,b(0) \sim 0
		\sim c(z)\,c(0)
	\end{equation}

	With the $bc$ OPE in hand, the $TT$ OPE is computed directly with brute force, by repeatedly applying Wick's theorem. This gives:
	\begin{equation}
		T(z)\,T(0)
		\sim \frac{
			-6\lambda^2 + 6\lambda - 1
		}{z^4} + \cdots
	\end{equation}
	In general we have $
		-6\lambda^2 + 6\lambda - 1
		= \frac{c}{2}
	$; for $\lambda = 2$ this gives $c = -26$. 
	\qedfull

@@

	\item[(b)(c)] Combining two $\psi$ expansions gives the mode expansion of $
		J\id{_i^j}
		= \normorder{\psi_i(z)\,\psi^j(z)}
	$, namely:
	\begin{equation}
		J\id{_i^j}(z)
		= \sum_{k\in\mbb{Z}}
			\frac{(J\id{_i^j})_k}{z^{k+1}},\quad
		(J\id{_i^j})_k
		= \sum_{q\in\mbb{Z}+\frac{1}{2}}
			\normorder{
				b_{iq}\,b^{j\dagger}_{k-q}
			}
	\end{equation}
	It is in fact more convenient to obtain the $JJ$ OPE first, and then use it to find the  $[J_0,J_0]$ mode commutator\footnote{
		I would like to thank \textit{谷夏} for providing this hint. 
	}; note that $
		{
			{\psi}_i(z)\,{\psi}^j(w)
		}
	$ contraction gives $\frac{\delta^j_i}{z-w}$, we have:
	\begin{equation}
		J\id{_i^j}(z)\,J\id{_k^l}(0)
		\sim \frac{
			\delta_i^l\delta_k^j
		}{z^2} + \frac{
			\delta^j_k J\id{_i^l}(0)
			- \delta^l_i J\id{_k^j}(0)
		}{z},\\[1ex]
		\bqty{
			(J\id{_i^j})_0, (J\id{_k^l})_0
		}
		= \frac{1}{(2\pi i)^2}
			\oint_0 \dd{w}
			\oint_w \dd{z}
				J\id{_i^j}(z)\,J\id{_k^l}(w)
		= \delta_i^l\,(J\id{_k^j})_0
			- \delta_k^j\,(J\id{_i^l})_0
	\end{equation}

	\item[(d)] Similar to $bc$ CFT, we have:
	\begin{equation}
		T(z) = \frac{1}{2}\,\pqty{
			\normorder{\psi_i\,\pd\psi^i}
			- \normorder{\pd\psi_i\,\psi^i}
		},\quad
		T(z)\,T(w)
		\sim \frac{n/2}{(z-w)^4}
			+ \frac{2T(w)}{(z-w)^2}
			+ \frac{\pd T(w)}{z-w}
	\end{equation}
	With each (complex) field contributing $\frac{1}{2}\times 2$ central charge\footnote{
		In fact a complex (Dirac) fermion can be ``treated like'' (\textit{dual to}) a boson; this is \textit{bosonization}. 
	}.

@@

	Similar holds for $J_{ij} = \normorder{\psi_i\psi_j}$ and its OPE, but we no longer need to distinguish upper/lower indices; we have:
	\begin{equation}
		J_{ij}(z)\,J_{kl}(0)
		\sim \frac{
			- \delta_{ik}\delta_{jl}
			+ \delta_{il}\delta_{jk}
		}{z^2} + \frac{
			- \delta_{ik} J_{jl}(0)
			+ \delta_{il} J_{jk}(0)
			+ \delta_{jk} J_{il}(0)
			- \delta_{jl} J_{ik}(0)
		}{z}\\[1ex]
		\bqty{
			(J_{ij})_0, (J_{kl})_0
		}
		= - \delta_{ik} (J_{jl})_0
			+ \delta_{il} (J_{jk})_0
			+ \delta_{jk} (J_{il})_0
			- \delta_{jl} (J_{ik})_0
	\end{equation}
	This is precisely the $\mfrak{o}(n)$ algebra. 
	\qedfull
